VIP-193: Committee-Based POA

### 2019-11-27 article.tex

\begin{equation}
    b_u^m \leftarrow H({\tt Sig}_{\,l_r}(\Gamma_{r})).
\end{equation}

Here we define $b_u^0=H(B_{\textrm{genesis}})$.

Beacon~$b_u^m$ is then used to calculate VRF messages for the next epoch. In particular, we compute message~${\tt M}_{\,r'}$ in round~$r'$ as:

@@

Now let us consider the case when the leader who generates $\hat{B}_{u,r}^{\,m}$ is malicious. Since signatures from the committee members are deterministic, the best he can do is to go through every combination of $d$ signatures and pick the one that maximizes his interest. The number of possible trials is fairly limited and therefore, we significantly limit the leader's influence on the beacon.

>>>>

\begin{equation}
    b_u^m \leftarrow H({\tt Sig}_{\,l_r}(\pi_{u_1,r}\,\|\,\pi_{u_1,r}\,\|\,\cdots\,\|\,\pi_{u_d,r})).
\end{equation}

Here we define $b_u^0\leftarrow H(B_{\textrm{genesis}})$. Beacon~$b_u^m$ is then used to calculate VRF messages for the next epoch. In particular, we compute message~${\tt M}_{\,r'}$ in round~$r'$ as:

@@

Now let us consider the case when the leader who generates $\hat{B}_{u,r}^{\,m}$ is malicious. Since signatures from the committee members are deterministic, the best he can do is to go through every combination of $d$ signatures from all the signatures he has received from committee members and pick the one that maximizes his interest. The number of possible trials is fairly limited and therefore, we significantly limit the leader's influence on the beacon.
